Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2017-01-30 paper1.tex
more edits.

\subsection{Conditional {\rm[\ion{O}{II}]} Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS Data Release 12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog. We use 503,113 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux signal-to-noise of at least five. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
\begin{lstlisting}[language=SQL]
SELECT GAL.objid, 
       GAL.u, 
       GAL.err_u, 
       GAL.g, 
       GAl.err_g, 
       GAL.r, 
       GAL.err_r, 
       GAL.i, 
       GAl.err_i, 
       GAL.z, 
       GAL.err_z, 
       g.oii_3726_flux, 
       g.oii_3726_flux_err, 
       s.z as redshift 
FROM   galaxy AS GAL 
       JOIN specobj AS s 
         ON s.bestobjid = GAL.objid 
       JOIN galspecline AS g 
         ON g.specobjid = s.specobjid 
WHERE  oii_3726_flux > oii_3726_flux_err * 5 
       AND oii_3726_flux_err > 0 
       AND s.class = 'GALAXY' 
       AND s.zwarning = 0 
\end{lstlisting}

@@

\begin{table*}
\centering
\caption[Mean bias for different bins of predicted cluster mass.]{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass. This table shows the bias in the predicted cluster mass for the Perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
\begin{tabular}{cccccccc} 
		&& \multic{6}{Bins -- Log $M_{pred}$} \\
		\cline{3-8} 
		\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
		\hline
&& \multic{6}{Perfect Observations} \\
\hline
\multicolumn{2}{c}{Power Law} & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
\hline 
\rottext{3}{Prob} &$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
&$\sigma, z$ & $0.17\pm{0.005}$ & $0.01\pm{0.003}$ & $-0.06\pm{0.002}$ & $-0.11\pm{0.015}$ & $-0.14\pm{0.012}$ & $-0.38\pm{0.159}$ \\
&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & \nd \\
\hline
\rottext{4}{ML} &$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
&$\sigma, z$ & $0.12\pm{0.005}$ & $-0.01\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.08\pm{0.004}$ & $-0.11\pm{0.012}$ & $-0.24\pm{0.076}$ \\
&$\sigma, N_{gal}$ & $0.04\pm{0.004}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.006}$ & $-0.08\pm{0.041}$ \\
&$\sigma, z, N_{gal}$ & $0.04\pm{0.003}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.001}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.005}$ & $-0.08\pm{0.043}$ \\
\hline

@@

\begin{table*}
\centering
\caption[Mean scatter in cluster mass after bias correction for different bins of predicted cluster mass.]{Mean scatter (Eqn.~\ref{eqn: scatter}) in cluster mass after bias correction for different bins of predicted cluster mass. This table shows the scatter in the predicted cluster mass for the Perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins. The different mass recovery methods are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass is over estimated when compared to the true cluster mass.}
\begin{tabular}{cccccccc} 
		&& \multic{6}{Bins -- Log $M_{pred}$} \\
		\cline{3-8} 
		\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
		\hline 
		&& \multic{6}{Perfect Observations} \\
		\hline
		\multicolumn{2}{c}{Power Law} & $0.34\pm{0.005}$ & $0.22\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.14\pm{0.008}$ & $0.11\pm{0.040}$ \\
		\hline 
		\rottext{3}{Prob} &$\sigma$ & $0.26\pm{0.004}$ & $0.20\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.16\pm{0.009}$ & $0.19\pm{0.071}$ \\
		&$\sigma, z$ & $0.23\pm{0.003}$ & $0.19\pm{0.002}$ & $0.16\pm{0.002}$ & $0.55\pm{0.010}$ & $0.16\pm{0.009}$ & $0.39\pm{0.143}$ \\
		&$\sigma, z, N_{gal}$ & $0.47\pm{0.007}$ & $0.14\pm{0.001}$ & $0.10\pm{0.001}$ & $0.54\pm{0.010}$ & \nd & \nd \\
		\hline
		\rottext{4}{ML}	&$\sigma$ & $0.29\pm{0.004}$ & $0.24\pm{0.002}$ & $0.21\pm{0.002}$ & $0.19\pm{0.004}$ & $0.18\pm{0.010}$ & $0.22\pm{0.081}$ \\
		&$\sigma, z$ & $0.24\pm{0.003}$ & $0.20\pm{0.002}$ & $0.18\pm{0.002}$ & $0.16\pm{0.003}$ & $0.16\pm{0.009}$ & $0.19\pm{0.068}$ \\
		&$\sigma, N_{gal}$ & $0.19\pm{0.003}$ & $0.14\pm{0.001}$ & $0.10\pm{0.001}$ & $0.08\pm{0.002}$ & $0.07\pm{0.004}$ & $0.10\pm{0.037}$ \\
		&$\sigma, z, N_{gal}$ & $0.17\pm{0.002}$ & $0.13\pm{0.001}$ & $0.10\pm{0.001}$ & $0.07\pm{0.001}$ & $0.07\pm{0.004}$ & $0.11\pm{0.039}$ \\
		\hline

>>>>

\subsection{Conditional {\rm[\ion{O}{II}]} Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS Data Release 12 \citep{Alam2015} catalogs to assign [\ion{O}{II}] emission line strengths to the galaxies in the Buzzard catalog. We use 503,094 objects classified as galaxies selected over $z = 0.02 - 0.2$ with {\sc zwarning $=0$} and a measured [\ion{O}{II}] line flux of at least one. Figure~\ref{fig: oii sdss} shows the color-magnitude diagram (CMD) of $M_r$ and $g-r$ for these galaxies, and the following SQL query selects the appropriate galaxies:
\begin{lstlisting}[language=SQL]
SELECT GAL.objid,
SELECT GAL.objid,
       GAL.u,
       GAL.err_u,
       GAL.g,
       GAl.err_g,
       GAL.r,
       GAL.err_r,
       GAL.i,
       GAl.err_i,
       GAL.z,
       GAL.err_z,
       g.oii_3726_flux,
       g.oii_3726_flux_err,
       s.z AS redshift
INTO   mydb.sdsstraining
FROM   galaxy AS GAL
       JOIN specobj AS s
         ON s.bestobjid = GAL.objid
       JOIN galspecline AS g
         ON g.specobjid = s.specobjid
WHERE  oii_3726_flux > oii_3726_flux_err
       AND oii_3726_flux_err > 0
       AND s.z BETWEEN 0.02 AND 0.2
       AND s.class = 'GALAXY'
       AND s.zwarning = 0
\end{lstlisting}

@@

\begin{table*}
\centering
\caption[Mean bias for different bins of predicted cluster mass.]{Mean bias (Eqn.~\ref{eqn: bias}) for different bins of predicted cluster mass. This table shows the bias in the predicted cluster mass for the Perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}
\begin{tabular}{cccccccc}
	\multic{8}{Mean Bias in the Recovered Cluster Mass Compared to the True Cluster Mass}\\
	\hline
	&& \multic{6}{Bins -- Log M$_{pred}/$\Msol} \\
	\cline{3-8}
	\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
	\hline
	&& \multic{6}{Perfect Observations} \\
	\hline
	\multicolumn{2}{c}{Power Law} & $0.23\pm{0.007}$ & $0.16\pm{0.003}$ & $0.11\pm{0.002}$ & $0.07\pm{0.004}$ & $0.02\pm{0.011}$ & $-0.07\pm{0.045}$ \\
	\hline
	\rottext{3}{Prob} &$\sigma$ & $0.32\pm{0.005}$ & $0.16\pm{0.003}$ & $0.10\pm{0.002}$ & $0.07\pm{0.004}$ & $0.05\pm{0.012}$ & $-0.18\pm{0.078}$ \\
	&$\sigma, z$ & $0.17\pm{0.005}$ & $0.01\pm{0.003}$ & $-0.06\pm{0.002}$ & $-0.11\pm{0.015}$ & $-0.14\pm{0.012}$ & $-0.38\pm{0.159}$ \\
	&$\sigma, z, N_{gal}$ & $0.04\pm{0.009}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.05\pm{0.014}$ & $-0.22\pm{0.126}$ & \nd \\
	\hline
	\rottext{4}{ML} &$\sigma$ & $0.14\pm{0.006}$ & $-0.01\pm{0.003}$ & $-0.07\pm{0.003}$ & $-0.09\pm{0.005}$ & $-0.11\pm{0.014}$ & $-0.17\pm{0.090}$ \\
	&$\sigma, z$ & $0.12\pm{0.005}$ & $-0.01\pm{0.003}$ & $-0.06\pm{0.003}$ & $-0.08\pm{0.004}$ & $-0.11\pm{0.012}$ & $-0.24\pm{0.076}$ \\
	&$\sigma, N_{gal}$ & $0.04\pm{0.004}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.006}$ & $-0.08\pm{0.041}$ \\
	&$\sigma, z, N_{gal}$ & $0.04\pm{0.003}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.001}$ & $-0.02\pm{0.002}$ & $-0.02\pm{0.005}$ & $-0.08\pm{0.043}$ \\
	\hline

@@

\begin{table*}
\centering
\caption[Mean scatter in cluster mass after bias correction for different bins of predicted cluster mass.]{Mean scatter (Eqn.~\ref{eqn: scatter}) in cluster mass after bias correction for different bins of predicted cluster mass. This table shows the scatter in the predicted cluster mass for the Perfect (top section), Targeted (middle section), and Survey (bottom section) observations in different predicted mass bins. The different mass recovery methods are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass is over estimated when compared to the true cluster mass.}
\begin{tabular}{cccccccc}
	\multic{8}{Mean Scatter in the Recovered Cluster Mass}\\
	\hline
	&& \multic{6}{Bins -- Log M$_{pred}/$\Msol} \\
	\cline{3-8}
	\multicolumn{2}{c}{Method} & $12.5-13$ & $13-13.5$ & $13.5-14$ & $14-14.5$ & $14.5-15$ & $15-15.5$ \\
	\hline
	&& \multic{6}{Perfect Observations} \\
	\hline
	\multicolumn{2}{c}{Power Law} & $0.34\pm{0.005}$ & $0.22\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.14\pm{0.008}$ & $0.11\pm{0.040}$ \\
	\hline
	\rottext{3}{Prob} &$\sigma$ & $0.26\pm{0.004}$ & $0.20\pm{0.002}$ & $0.16\pm{0.002}$ & $0.14\pm{0.003}$ & $0.16\pm{0.009}$ & $0.19\pm{0.071}$ \\
	&$\sigma, z$ & $0.23\pm{0.003}$ & $0.19\pm{0.002}$ & $0.16\pm{0.002}$ & $0.55\pm{0.010}$ & $0.16\pm{0.009}$ & $0.39\pm{0.143}$ \\
	&$\sigma, z, N_{gal}$ & $0.47\pm{0.007}$ & $0.14\pm{0.001}$ & $0.10\pm{0.001}$ & $0.54\pm{0.010}$ & \nd & \nd \\
	\hline
	\rottext{4}{ML}	&$\sigma$ & $0.29\pm{0.004}$ & $0.24\pm{0.002}$ & $0.21\pm{0.002}$ & $0.19\pm{0.004}$ & $0.18\pm{0.010}$ & $0.22\pm{0.081}$ \\
	&$\sigma, z$ & $0.24\pm{0.003}$ & $0.20\pm{0.002}$ & $0.18\pm{0.002}$ & $0.16\pm{0.003}$ & $0.16\pm{0.009}$ & $0.19\pm{0.068}$ \\
	&$\sigma, N_{gal}$ & $0.19\pm{0.003}$ & $0.14\pm{0.001}$ & $0.10\pm{0.001}$ & $0.08\pm{0.002}$ & $0.07\pm{0.004}$ & $0.10\pm{0.037}$ \\
	&$\sigma, z, N_{gal}$ & $0.17\pm{0.002}$ & $0.13\pm{0.001}$ & $0.10\pm{0.001}$ & $0.07\pm{0.001}$ & $0.07\pm{0.004}$ & $0.11\pm{0.039}$ \\
	\hline
